Regression for correlated variables : application in steel industry

### 2014-01-24 www/Rennes.tex
resultats
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@272 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass[12pt]{article}
%
%
% Retirez le caractere "%" au debut de la ligne ci--dessous si votre
% editeur de texte utilise des caracteres accentues
\usepackage[utf8]{inputenc}
%
% Retirez le caractere "%" au debut des lignes ci--dessous si vous
% utiisez les symboles et macros de l'AMS
\usepackage{amsmath}
\usepackage{amsfonts}
%
%
\setlength{\textwidth}{16cm}
\setlength{\textheight}{21cm}
\setlength{\hoffset}{-1.4cm}
%
%
\begin{document}

@@

We note that (\ref{MainR}) and (\ref{SR}) also give :
\begin{eqnarray}
	Y&=&X^{I_2^c} (A_{I_2^c}+ \sum_{j \in I_2}B^{j}_{I_1}A_{j})+  \sum_{j \in I_2}\varepsilon_{j}A_{j}+\varepsilon_Y \\
					&=& X^{I_2^c}\tilde{A}_{I_2^c}+ \tilde{\varepsilon}=X\tilde{A}+ \tilde{\varepsilon}\label{Trueexpl} \\
			\textrm{where }		\tilde{A}_{I_2}&=&0 \\
					\tilde{A}_{I_2^c}&=&A_{I_2^c}+ \sum_{j \in I_2}B^{j}_{I_1}A_{j} 
\end{eqnarray}
\section{Estimateur}
	Classical methods like Ordinary Least Squares (OLS) estimate $Y|X$ and obtain (Maximum Likelihood Estimation): 
		\begin{equation}
			\hat A = (X'X)^{-1}X'Y \textrm{ (ill-conditoned matrix to inverse)}
		\end{equation}
		With following properties :
		\begin{eqnarray}
			E[\hat{A}|X]&=&A \\
			Var[\hat{A}|X]&=& \sigma_Y^2(X'X)^{-1}
		\end{eqnarray}				
		And when correlations are strong, the matrix to invert is ill-conditioned and the variance explodes.

@@

			When we use a variable selection method on it we obtain two kinds of 0 :
			\begin{enumerate}
			\item Because of the structure we coerce $\hat{\tilde{A}}^{I_2} = 0 $. This kind of zero means redundant information but the covariate can be correlated with the response variable. So we don't have the grouping effect (so we are more parsimonious ) and we don't suffer from false interpretation (LASSO would).
			\item Variable selection methods can lead to get some exact zeros in $\hat{\tilde{A}}^{I_1}$. This kind of zero means that implied covariate has no significant effect on the response variable. And because variables in $X^{I_1}$ are orthogonal, we know that it is not misleading interpretation due to correlations.
			\end{enumerate}
\section{Recherche de structure}

@@

\section{Résultats}	
\section{Conclusion et perspectives}
	CorReg est fonctionnel et disponible
	Besoin d'élargir à la gestion des valeurs manquantes très présentes dans l'industrie
\section{Exemple de références bibliographiques}
La nécessité de produire des résumés clairs et bien
référencés aété démontrée par Achin et Quidont~(2000). Le
récent article de Noteur~(2003) met enévidence \dots

>>>>

\documentclass[12pt]{article}
%
%
% Retirez le caractere "%" au debut de la ligne ci--dessous si votre
% editeur de texte utilise des caracteres accentues
\usepackage[utf8]{inputenc}
%
% Retirez le caractere "%" au debut des lignes ci--dessous si vous
% utiisez les symboles et macros de l'AMS
\usepackage{amsmath}
\usepackage{amsfonts}
%
%
\setlength{\textwidth}{16cm}
\setlength{\textheight}{21cm}
\setlength{\hoffset}{-1.4cm}
%
%
\usepackage{graphicx}

 \graphicspath{{figures/}}

\begin{document}

@@

We note that (\ref{MainR}) and (\ref{SR}) also give :
\begin{eqnarray}
	Y&=&X^{I_2^c} (A_{I_2^c}+ \sum_{j \in I_2}B^{j}_{I_1}A_{j})+  \sum_{j \in I_2}\varepsilon_{j}A_{j}+\varepsilon_Y \\
					&=& X^{I_2^c}\tilde{A}_{I_2^c}+ \tilde{\varepsilon}=X\tilde{A}+ \tilde{\varepsilon}\label{Trueexpl} 			
\end{eqnarray}
\section{Estimateur}
	Classical methods like Ordinary Least Squares (OLS) estimate $Y|X$ and obtain (Maximum Likelihood Estimation): 
		\begin{equation}
			\hat A = (X'X)^{-1}X'Y \textrm{ (ill-conditoned matrix to inverse)}
		\end{equation}
		With following properties :
		\begin{eqnarray}
			E[\hat{A}|X]&=&A \\
			Var[\hat{A}|X]&=& \sigma_Y^2(X'X)^{-1}
		\end{eqnarray}				
		And when correlations are strong, the matrix to invert is ill-conditioned and the variance explodes.

@@

			When we use a variable selection method on it we obtain two kinds of 0 :
			\begin{enumerate}
			\item Because of the structure we coerce $\hat{\tilde{A}}^{I_2} = 0 $. This kind of zero means redundant information but the covariate can be correlated with the response variable. So we don't have the grouping effect (so we are more parsimonious ) and we don't suffer from false interpretation (LASSO would~\cite{Zhao2006MSC}).
			\item Variable selection methods can lead to get some exact zeros in $\hat{\tilde{A}}^{I_1}$. This kind of zero means that implied covariate has no significant effect on the response variable. And because variables in $X^{I_1}$ are orthogonal, we know that it is not misleading interpretation due to correlations.
			\end{enumerate}
\section{Recherche de structure}

@@

\section{Résultats}

Some observed correlations with physical meaning :
			\begin{itemize}
				\item Width and Weight : 0.905
				\item Temperature before and after a tool : 0.983 
				\item Roughness of both faces : 0.919
				\item Mean \& Max of a curve : 0.911
			\end{itemize}

Some found subregressions with physical meaning :
			\begin{itemize}
				\item Mean.weight = f (Min.weight , Max.weight , Sigma.weight ) and other same-shaped subregressions.
				\item Width = f (Mean.flow , Mean.speed.CC)

True Physical model (not linear) :\begin{itemize}
\item Width = flow / (speed * thickness) (thickness is constant)
\end{itemize} 
			\end{itemize}

			Some of the other subregression represent physical models used to regulate the process and that were forgotten by the metallurgist we worked with.

Exemple détaillé :

		\begin{figure}	
		\centering		
			\includegraphics[width=100px]{figures/histcor_auchan.JPG} 
			\caption{Histogramme des corrélations observées (117 individus pour 168 variables)}
		\end{figure}

\section{Conclusion et perspectives}
	CorReg est fonctionnel et disponible
	Besoin d'élargir à la gestion des valeurs manquantes très présentes dans l'industrie
\section{Exemple de références bibliographiques}
La nécessité de produire des résumés clairs et bien
référencés aété démontrée par Achin et Quidont~(2000). Le
récent article de Noteur~(2003) met enévidence \dots
